---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ceblR

<!-- badges: start -->
[![R-CMD-check](https://github.com/awosoga/ceblR/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/awosoga/ceblR/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of ceblR is to help interested parties scrape and analyze data from the 
Canadian Elite Basketball League. It provides functions to present data in an 
easy-to-use format provides greater detail an accessibility than what is included
on the official [CEBL Website](https://cebl.ca)

## Installation

You can install the development version of ceblR from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("awosoga/ceblR")
```

## Usage

```{r example}
library(ceblR)
## basic example code
```
