---
title: "How to use ceblR"
author: "David Awosoga"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ceblR-how-to-use}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  comment = "#>"
)
```

## Overview

This vignette will outline how to use the functions in the `ceblR` package 
to access data from the Canadian Elite Basketball League (CEBL).

## Installation

You can install the development version of [**```ceblR```**](https://github.com/awosoga/ceblR) from [GitHub](https://github.com/awosoga/ceblR) with:

```{r installation, eval=FALSE}
# install.packages("remotes")
remotes::install_github("awosoga/ceblR")
```

```{r setup}
library(ceblR)
library(dplyr)
```

## Usage

The following code snippets will provide information on how to access different CEBL statistics.

### Team Boxscores

Use `team_boxscore_data()` to access team boxscore outputs.

```{r team_boxscores}
team_boxscores <- team_boxscore_data(2020)
glimpse(team_boxscores)
```

### Player Boxscores

Use `player_boxscore_data()` to access individual player boxscore outputs.

```{r player_boxscores}
player_boxscores <- player_boxscore_data(2020)
glimpse(player_boxscores)
```

### Advanced Player Data

Use `player_advanced_data()` to access individual advanced statistics such as [*Player Efficiency Rating*](https://www.basketball-reference.com/about/per.html) (**PER**),
[*Box Plus Minus*](https://www.basketball-reference.com/about/bpm2.html) (**BPM**), and [*Value Over Replacement Player*](https://www.basketball-reference.com/about/bpm2.html) (**VORP**). Note that all calculations are unofficial.

```{r advanced_player_data}
player_advanced_data <- player_advanced_data(2020)
glimpse(player_advanced_data)
```

### Advanced Team Data

Use `team_advanced_data()` to access team advanced statistics such as *Pace*, 
*Offensive* and *Defensive Rating*, and the [*Four Factors*](https://www.basketball-reference.com/about/factors.html). Note that all calculations are unofficial.

```{r advanced_team_data}
team_advanced_data <- team_advanced_data(2020)
glimpse(team_advanced_data)
```


